Proving linearizability using forward simulations

### 2017-01-25 draftCAV/app-tss.tex
fixed a typo

For the cases $\alpha' = \alpha$, we first need to show $\alpha'$ is enabled in state $t$ i.e., $t$ satisfies $\psi'$. If this can not be directly obtained from the information that $s$ satisfies $\psi$ and using one or two obvious conditions on $\mathit{fs}_2$ (since $t \in \mathit{fs}_2[s]$), we show the derivation in the proof. Then, $t'$ is obtained in a unique way since $AbsS$ is deterministic on its alphabet $ \Sigma_{AbsS} = C \cup R \cup Com(pop)$. The, only other thing to show is $t' \in \mathit{fs}_2[t']$. We show this by proving that $t'$ does not violate any of the conditions of the $\mathit{fs}_2$ described above. Suppose conditions on $\mathit{fs}_2$ are of the form $\forall \overline{k}. guard_{s,t}(\overline{k}) \triangleright \phi_{s,t}(\overline{k})$ where the $overline{k}$ is a vector of operation identifiers and $\phi$ defined on states $s$ and $t$ must hold if the guard defined on $s$ and $t$ holds. We say that a vector $\overline{k_1}$ is a new instantiation of the condtion if $\overline{k_1}$ not satisfy the $guard_{s,t}$ while relating pre-states, but it satisfies $guard_{s',t'}$ while relating post-states and $\phi_{s',t'}$ needs to be checked non-trivially.

>>>>

For the cases $\alpha' = \alpha$, we first need to show $\alpha'$ is enabled in state $t$ i.e., $t$ satisfies $\psi'$. If this can not be directly obtained from the information that $s$ satisfies $\psi$ and using one or two obvious conditions on $\mathit{fs}_2$ (since $t \in \mathit{fs}_2[s]$), we show the derivation in the proof. Then, $t'$ is obtained in a unique way since $AbsS$ is deterministic on its alphabet $ \Sigma_{AbsS} = C \cup R \cup Com(pop)$. The, only other thing to show is $t' \in \mathit{fs}_2[t']$. We show this by proving that $t'$ does not violate any of the conditions of the $\mathit{fs}_2$ described above. Suppose conditions on $\mathit{fs}_2$ are of the form $\forall \overline{k}. guard_{s,t}(\overline{k}) \triangleright \phi_{s,t}(\overline{k})$ where the $\overline{k}$ is a vector of operation identifiers and $\phi$ defined on states $s$ and $t$ must hold if the guard defined on $s$ and $t$ holds. We say that a vector $\overline{k_1}$ is a new instantiation of the condtion if $\overline{k_1}$ does not satisfy the $guard_{s,t}$ while relating pre-states, but it satisfies $guard_{s',t'}$ while relating post-states.
